Probabilistic Forecast Reconciliation

### 2018-06-05 Presentation/Figs/probforerec_schematic.tex
Added Presentation

% Created by tikzDevice version 0.11 on 2018-04-20 18:17:41
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (505.89,361.35);
\begin{scope}
\path[clip] ( 49.20, 61.20) rectangle (480.69,312.15);
\definecolor{drawColor}{RGB}{0,0,0}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (229.69, 68.00) {{\huge $\color{red}{s(\mathcal{B})}$}};
\definecolor{drawColor}{RGB}{255,0,0}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (370.70,215.86) {{\huge $\color{blue}{g^{-1}(\mathcal{B}})$}};

>>>>

% Created by tikzDevice version 0.11 on 2018-04-24 21:50:28
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=0.6pt,y=0.6pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (505.89,361.35);
\begin{scope}
\path[clip] ( 49.20, 61.20) rectangle (480.69,312.15);
\definecolor{drawColor}{RGB}{0,0,0}

@@

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (244.09, 68.20) {{\huge $\color{red}{s(\mathcal{B})}$}};
\definecolor{drawColor}{RGB}{255,0,0}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (370.70,232.76) {{\huge $\color{blue}{g^{-1}(\mathcal{B}})$}};
